\documentclass[margin,a4paper]{res}
\addtolength{\topmargin}{-.5in}
\addtolength{\oddsidemargin}{-.0in}
\addtolength{\textheight}{2.0in}
\setlength{\textwidth}{5.3in} % set width of text portion

\usepackage{hyperref}
\usepackage{graphicx}

\begin{document}

 \moveleft.5\hoffset\centerline{\large\bf Abdullah Alrajeh}
 \moveleft\hoffset\vbox{\hrule width \resumewidth height 1pt}\smallskip
 \moveleft.5\hoffset\centerline{E-mail : asrajeh@kacst.edu.sa}
 \moveleft.5\hoffset\centerline{Website: https://asrajeh.github.io/}
 
\begin{resume}

\section{PERSONAL \\ INFORMATION} Nationality: Saudi Arabia \scalebox{4.0}{.} Gender: Male \scalebox{4.0}{.} Languages: Arabic/English\\

\section{EDUCATION}
		{\bf University of Southampton, UK (2015)}

		Ph.D., Computer Science, ECS, Faculty of Physical Sciences and Engineering

		Thesis: {\sl Large-scale Reordering Models for Statistical Machine Translation}

		{\bf University of Manchester, UK (2009)}

		M.Sc., Advanced Computer Science, School of Computer Science

		Thesis: {\sl Prediction of Polymorphic Form from Experimental and Theoretical Data}

		Courses: Machine Learning \scalebox{4.0}{.} High Performance Computing \scalebox{4.0}{.} Advanced Machine Vision \scalebox{4.0}{.} Advanced Database Management Systems \scalebox{4.0}{.} The Semantic Web: Ontologies and OWL \scalebox{4.0}{.} Computer Animation
		
		{\bf King Saud University, Saudi Arabia (2006)}

		B.Sc., Computer Science, College of Computer and Information Sciences


\section{RESEARCH\\INTERESTS} 
{\bf machine learning} 

classification, structured prediction, probabilistic modeling, deep learning

{\bf machine translation}

phrase-based machine translation, neural machine translation

{\bf speech processing}

speech recognition, speaker recognition, language identification, speech synthesis
 
{\bf image processing}

optical character recognition, object recognition

\section{PROFESSIONAL\\EXPERIENCE} 
Assistant Research Professor at the National Center for Artificial intelligence and Big Data Technology-KACST since 2015.

Researcher A at the Computer Research Institute-KACST (2009-2015).

Researcher at the Computer Research Institute-KACST (2006-2009).

\section{TECHNICAL\\EXPERIENCE} {\sl OS Systems:}
				\begin{itemize}
				\item Linux (Ubuntu, Debian, CentOS) and Mac
				\end{itemize}

				{\sl Software and Libraries:}
				\begin{itemize}
				\item Moses, Nematus, Marian, Kaldi, Merlin, Mycroft, TensorFlow and OpenCV
				\end{itemize}

				{\sl Programming Languages:}
				\begin{itemize}
				\item C, C++, Java, AWK, Perl, Python, HTML, JavaScript, SQL, PHP and CUDA
				\end{itemize}

				{\sl Tools:}
				\begin{itemize}
		 		\item  LaTeX, MATLAP, GDB, Grid Engine, SLURM, MySQL and Apache Server
				\end{itemize}
\section{PROJECTS}
Arabic Virtual Assistant

Arabic Speech Recognition

Hebrew-Arabic Machine Translation

Arabic Text Classification

Arabic Optical Character Recognition

Arabic Optical Braille Recognition

\section{PEER\\REVIEW}
The 2021 Conference on Empirical Methods in Natural Language Processing (EMNLP)

Journal of King Saud University - Computer and Information Sciences

Arabian Journal for Science and Engineering

\section{CONFERENCE\\COMMITTEES} 

The 4th Saudi International Conference on Information Technology: Big Data Analysis (November 2016)

The Saudi Arabian High Performance Computing Conference and Exhibition (April 2016)


\section{PUBLICATIONS}
{\bf Alrajeh, A.} (2018) A Recipe for Arabic-English Neural Machine Translation. Computing Research Repository, arXiv:1808.06116.

{\bf Alrajeh, A.} and Niranjan, M. (2015) Scalable reordering models for SMT based on multiclass SVM. The Prague Bulletin of Mathematical Linguistics.

{\bf Alrajeh, A.} and Niranjan, M. (2015) Generative and discriminative reordering models for statistical machine translation. In, 8th Saudi Students Conference, UK.

{\bf Alrajeh, A.} and Niranjan, M. (2014) Bayesian reordering model with feature selection. In, ACL: 9th WMT, USA.

{\bf Alrajeh, A.} and Niranjan, M. (2014) Large-scale Reordering Model for Statistical Machine Translation using Dual Multinomial Logistic Regression. In, EMNLP, Qatar.

{\bf Alrajeh, A.}, Takeda, A. and Niranjan, M. (2014) Memory-efficient Large-scale Linear Support Vector Machine. In, 7th ICMV, Italy.

Al-Harbi, S, Almuhareb, A, Al-Thubaity , A, Khorsheed, M. S. and {\bf Al-Rajeh, A} (2008) Automatic Arabic Text Classification. In, 9th ICSATD, France.

Althubaity, A., Almuhareb, A., Alharbi, S., {\bf Al-Rajeh, A.} and Khorsheed , M. (2008) KACST Arabic Text Classification Project: Overview and Preliminary Results. In, 9th IBIMA, Morocco.

Al-Salman, A., AlOhali, Y. , AlKanhal, M. and {\bf AlRajih, A.} (2007) An Arabic Optical Braille Recognition System. In, ICTA, Tunisia.

\end{resume}
\end{document}
