\documentclass[margin,a4paper]{res}
\addtolength{\topmargin}{-.5in}
\addtolength{\oddsidemargin}{-.0in}
\addtolength{\textheight}{2.0in}
\setlength{\textwidth}{5.3in} % set width of text portion
\usepackage{hyperref}
\usepackage{graphicx}



\begin{document}

\begin{resume}

\section{PERSONAL \\ INFORMATION} Nationality: Saudi Arabia \scalebox{4.0}{.} Gender: Male \scalebox{4.0}{.} Languages: Arabic/English\\

\section{EDUCATION}
		{\bf University of Southampton, UK (2015)}\\
		Ph.D., Computer Science, ECS, Faculty of Physical Sciences and Engineering\\
		Thesis: {\sl Large-scale Reordering Models for Statistical Machine Translation}

		{\bf University of Manchester, UK (2009)}\\
		M.Sc., Advanced Computer Science, School of Computer Science\\
		Thesis: {\sl Prediction of Polymorphic Form from Experimental and Theoretical Data}\\
		Courses: Machine Learning \scalebox{4.0}{.} High Performance Computing \scalebox{4.0}{.} Advanced Machine Vision \scalebox{4.0}{.} Advanced Database Management Systems \scalebox{4.0}{.} The Semantic Web: Ontologies and OWL \scalebox{4.0}{.} Computer Animation
		
		{\bf King Saud University, Saudi Arabia (2006)}\\
		B.Sc., Computer Science, College of Computer and Information Sciences


\section{RESEARCH\\INTERESTS} Machine Learning; Deep Learning; Machine Translation; Speech Recognition
\vspace{.1in}

\section{PROFESSIONAL\\EXPERIENCE} I have worked as a researcher for the Computer Research Institute at King Abdulaziz City for Science and Technology (KACST) since 2006.

\section{PEER\\REVIEW}  The 2021 Conference on Empirical Methods in Natural Language Processing (EMNLP)\\
		 	Journal of King Saud University - Computer and Information Sciences\\
			Arabian Journal for Science and Engineering
\section{TECHNICAL\\EXPERIENCE} {\sl Software:} Moses, cdec, Cambridge system, Nematus and Kaldi\\
				{\sl Programming Languages:} C, C++, Java, AWK, Perl, Python, SQL and PHP\\
				{\sl Tools:} LaTeX, Eclipse, MATLAP, Octave, Netlab, Weka, JDeveloper and Hadoop

\section{PUBLICATIONS}
{\bf Alrajeh, A.} (2018) A Recipe for Arabic-English Neural Machine Translation. Computing Research Repository, arXiv:1808.06116.

{\bf Alrajeh, A.} and Niranjan, M. (2015) Scalable reordering models for SMT based on multiclass SVM. The Prague Bulletin of Mathematical Linguistics.

{\bf Alrajeh, A.} and Niranjan, M. (2015) Generative and discriminative reordering models for statistical machine translation. In, 8th Saudi Students Conference, UK.

{\bf Alrajeh, A.} and Niranjan, M. (2014) Bayesian reordering model with feature selection. In, ACL: 9th WMT, USA.

{\bf Alrajeh, A.} and Niranjan, M. (2014) Large-scale Reordering Model for Statistical Machine Translation using Dual Multinomial Logistic Regression. In, EMNLP, Qatar.

{\bf Alrajeh, A.}, Takeda, A. and Niranjan, M. (2014) Memory-eﬃcient Large-scale Linear Support Vector Machine. In, 7th ICMV, Italy.

Al-Harbi, S, Almuhareb, A, Al-Thubaity , A, Khorsheed, M. S. and {\bf Al-Rajeh, A} (2008) Automatic Arabic Text Classification. In, 9th ICSATD, France.

Althubaity, A., Almuhareb, A., Alharbi, S., {\bf Al-Rajeh, A.} and Khorsheed , M. (2008) KACST Arabic Text Classification Project: Overview and Preliminary Results. In, 9th IBIMA, Morocco.

Al-Salman, A., AlOhali, Y. , AlKanhal, M. and {\bf AlRajih, A.} (2007) An Arabic Optical Braille Recognition System. In, ICTA, Tunisia.

\end{resume}
\end{document}
